04_DESeq_sexes

### 2019-08-28 analysis/04_DESeq2_sexes.Rmd
adding total degs back
added total degs, but eval is false for now, too long to run
now with temporary screenshot plot
replace dds with vsd PCA
name to vsd.df instead of DEGs, remove repeated code

```{r setup, message=F, comment=FALSE, warning=FALSE, results='hide'}

@@

@@

```{r vsd}

>>>>

```{r setup, include = FALSE}

@@

## total degs

```{r totalDEGs, results = 'hide', eval = F}
DEGs.pituitary <- returntotalDEGs(dds.pituitary)
plottotalDEGs(DEGs.pituitary, "Male & Female Pituitary DEGs")
```

@@

```{r vsd}
vsd.hyp <- vst(dds.hypothalamus, blind=FALSE) 
vsd.pit <- vst(dds.pituitary, blind=FALSE) 
vsd.gon <- vst(dds.gonad, blind=FALSE)

vsd.hyp.df <- vsd.dataframe(vsd.hyp) 
vsd.pit.df <- vsd.dataframe(vsd.pit) 
vsd.gon.df <- vsd.dataframe(vsd.gon) 
```
